Pesticides pollution of small streams in Germany

### 2016-07-21 article.tex
update

@@

We homogenized and unified these datasets into a common database.
We implemented a robust and transparent data cleaning work flow \citep{poisot_best_2015}, though parts of the dataset are proprietary.
An overview of the data cleaning process is provided in the supplemental materials.  
The compiled dataset comprised only a small fraction of standing waters and most of the samples where sampled via grab sampling.
Therefore, we report  only results for grab sampling from streams.  \todo{move to results and say that nearly no information on standing waters is available}
To assess whether  grab samples were taken during potential rainfall events we intersected sampling coordinates and date with daily precipitation data \citep{rauthe_central_2013}.

@@

\item Regulatory Acceptable Concentrations (RAC) \citep{brock_linking_2010}:
This is the lowest concentration at which no acceptable biological effects are expected. 
These are derived during regulatory approval  process of pesticides and contains a uncertainty factor.
The German Federal Environmental Agency provided RACs for this study.

@@

Were $C_i$ is the concentration of compound $i$ in a sample and $EC_{50, D.magna, i}$ is the concentration of this compound where 50\% of the exposed animals showed after 48 hours an effect in a laboratory study.
We compiled $EC_{50, D.magna}$ values from literature \citep{malaj_organic_2014}, databases \citep{pesticide_action_network_pan_2015,u.s._epa_ecotoxicology_2015} or model predictions \citep{schuurmann_quantitative_2011}, where experimental data had priority.
We used the maximum TU per sample, as it is independent of the number of measured compounds and makes no assumptions on the mode of action.
\end{enumerate}

@@

@@

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/fig1.pdf}
  \caption{Map of the 3109 sampling sites. Colour codes different federal states.}
  \label{fig:fig1}
\end{figure}

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/ezg_lu.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points
  }
  \label{fig:fig_ezg_lu}
\end{figure}

>>>>

More than 50\% of the total land area in Germany are used by agriculture \citep{statistisches_bundesamt_bodenflache_2014}.
In the year 2014 more the 45000 tonnes of 766 authorized pesticides were sold for application on these areas \citep{bundesamt_fur_verbraucherschutz_und_lebensmittelsicherheit_absatz_2015}.
The applied pesticides may enter surface waters via spray-drift, edge-off-field run-off or drainage, with run-off being one of the major input routes \citep{schulz_comparison_2001}.
Once entered the surface waters pesticides are frequently detected in environmental monitoring \citep{malaj_organic_2014} and may have adverse effects on biota and ecosystem functioning \citep{schulz_field_2004, schafer_effects_2007}.

@@

We homogenized and unified these datasets into a common database.
We implemented a robust and transparent data cleaning work flow \citep{poisot_best_2015}, though parts of the dataset are proprietary.
An overview of the data cleaning process is provided in the supplemental materials.  
The compiled dataset comprised only a small fraction of standing waters and most of the samples where sampled via grab sampling.
Therefore, we report  only results for grab sampling from streams.  \todo{move to results and say that nearly no information on standing waters is available}
To assess whether  grab samples were taken during potential rainfall events we intersected sampling coordinates with daily precipitation data \citep{rauthe_central_2013} from the sampling date and the day before .

@@

\item Regulatory Acceptable Concentrations (RAC) \citep{brock_linking_2010}:
This is the lowest concentration at which no acceptable biological effects are expected. 
These are derived during authorization  process of pesticides and contain an uncertainty factor.
The German Federal Environmental Agency provided RACs for this study.  
We expressed  RAC as Risk Quotient (RQ)

\begin{equation}
RQ = \frac{C}{RAC}
\end{equation}

Where $C$ is the concentration of a compound in a sample.

@@

Where $C_i$ is the concentration of compound $i$ in a sample and $EC_{50, D.magna, i}$ is the concentration of this compound where 50\% of the exposed animals showed after 48 hours an effect in a laboratory study.
We compiled $EC_{50, D.magna}$ values from literature \citep{malaj_organic_2014}, databases \citep{pesticide_action_network_pan_2015,u.s._epa_ecotoxicology_2015} or model predictions \citep{schuurmann_quantitative_2011}, where experimental data had priority.
We used the maximum TU per sample, as it is independent of the number of measured compounds and makes no assumptions on the mode of action.
A table of all included compounds can be found in the supplement.
\end{enumerate}

@@

We used Multidimensional Scaling (MDS) based on jeccard dissimilarity in conjunction with hierarchical clustering to display differences in the spectra of analysed compounds per federal state.

@@

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/fig1.pdf}
  \caption{Spatial distribution of the 3109 sampling sites. Colour codes different federal states.}
  \label{fig:fig1}
\end{figure}

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/ezg_lu.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points.
  }
  \label{fig:fig_ezg_lu}
\end{figure}
